% +--------------------------------------------------------------------+
% | Acknowledgements Page (Optional)
% +--------------------------------------------------------------------+

\newpage
\vspace*{0.9cm}
\begin{center}
{\bf \Huge Acknowledgments}
\end{center}

\setlength{\baselineskip}{0.8cm}

%\pdfbookmark[0]{Acknowledgements}{PDF_Acknowledgements}

% +--------------------------------------------------------------------+
% | Enter text for your acknowledgements in the space below this box.
% |                                                                    
% +--------------------------------------------------------------------+

First and foremost, I thank my advisor Dr. Virginia Naibo. I am forever grateful for the enormous amount of time she spent meeting with me to discuss the results in this work, review notes and slides for presentations, and provide helpful criticisms and advice. Additionally, she has been my best role model as a researcher and teacher. I know that without her mentoring, insights, and boundless patience this work would not have been possible.

I also thank everyone else who served on my supervisory committee. My thanks go to Dr. Nathan Albin, Dr. Hrant Hakobyan, and Dr. Anna Zemlyanova for serving on this committee and being wonderful examples to me. Many thanks to Dr. Ryszard Jankowiak for accepting my request to serve on my supervisory committee. Thank you to Dr. James Neill for serving as the outside chairperson of my supervisory committee. 

Special thanks to Dr. Andrew Bennett for being the Mathematics Department head and Dr. Sarah Reznikoff for serving as the graduate student director. Thank you for all of the opportunities that you have provided for me and other graduate students.

Lastly, I thank all of my friends and family who supported my through my time as a graduate student. In particular, a huge thank you to my parents and wife who constantly encouraged me through this process. I am forever grateful for your generosity, encouragement, and even interest in my work.